Making all equalities equal

### 2021-09-09 paper.lagda.tex
solved TODO ~ problem
fixed grammar mistakes

In the begin of Agda and in most theorems proves, the equality is given by Martin-Löf's definition:

@@

This equality is very covenient in proof assistances like Agda, because it is possible to pattern match using them:

@@

To solve this problem, Agda adopted cubical type theory that equality is a function from path to types:

@@

The operator TODO-invert revert the interval. If the interval \AgdaBound{i} goes from
\AgdaBound{i0} to \AgdaBound{i1}, the interval TODO-invert-i goes from \AgdaBound{i1} to \AgdaBound{i0}.

@@

All equalities have something in common. They are all equal to each other.
So it will be defined a common record that all equalities should have.
In the next defintion, all equalities are equal to the cubical equality:

>>>>

At the begin of Agda and in most theorems proves, equality is given by Martin-Löf's definition:

@@

This equality is very convenient in proof assistances like Agda because it is possible to pattern match using them:

@@

To solve this problem, Agda adopted cubical type theory that equality is a function from the path to type:

@@

The operator $\sim$ invert the interval. If the interval \AgdaBound{i} goes from
\AgdaBound{i0} to \AgdaBound{i1}, the interval $\sim i$ goes from \AgdaBound{i1} to \AgdaBound{i0}.

@@

All equalities have something in common. They are all equal to each other.
So it will be defined as a common record that all equalities should have.
In the next definition, all equalities are equal to cubical equality:
